---
title: "`r print(RmdTitle);`"
author: "Marwin"
date: "`r format(Sys.time(), '%d %b %Y at %H:%M:%S');`"
output:
  html_document:
    toc: true
---

This is a test of the commits.

This is the report of the self-identity analyses for dataset '`r cat(dataframeName);`'.

```{r echo=FALSE}

require('userfriendlyscience')
safeRequire('ggplot2');
safeRequire('psych');
safeRequire('pander');
safeRequire('qgraph');
safeRequire('semPlot');

options(width=160);
options(xtable.type="html");
panderOptions('knitr.auto.asis', FALSE);
panderOptions('table.split.table', Inf);

pander.associationMatrix <- function(x) {
  pander(x$output$matrix$full);
}

```

## Descriptives

```{r results="asis", fig.width=6, fig.height=4 }

  ### For every variable in the dataset

  nonStringVariables <- !unlist(lapply(dat, is.character));

  pander(describe(dat[, nonStringVariables]));
  
  ### Uitgebreidere descriptives; descr works for vectors, so pass each
  ### column (variable) separately using lapply
  invisible(lapply(dat[, names(scales)], function(x) {
    pander(descr(x));
    print(dataShape(x)$plot);
  }));

```

### Scatter matrices between intention and scale items

```{r fig.width=8, fig.height=12}

  ### Generate a list containing scattermatrices of the associations
  ### between intention and each of the items in the other scales
  scatterMatricesObject <- list();
  for (currentScale in names(scales)[names(scales) != 'intention']) {
    cat0("\nCurrently processing '", currentScale, "'\n");
    scatterMatricesObject[[paste0("Intention With ", currentScale)]] <-
      paginatedAsymmetricalScatterMatrix(dat,
                                         rows = scales[[currentScale]],
                                         cols = scales$intention,
                                         maxRows = 4,
                                         showCorrelations=c('top-left',
                                                            'bottom-right'));
    print(scatterMatricesObject[[paste0("Intention With ", currentScale)]]$output$scatterMatrices);
  }

```

### Scale structure

```{r fig.width=16, fig.height=16}

  ### Order scale structure descriptives
  scaleStructureObject <- list();
  for (currentScale in names(scales)[names(scales) != 'currentBehavior']) {
    cat0("\nCurrently processing '", currentScale, "'\n");
    scaleStructureObject[[paste0("Scale Structure for ", currentScale)]] <-
      scaleStructure(dat, scales[[currentScale]], poly=FALSE);
    pander(associationMatrix(dat[, scales[[currentScale]]]));
    print(scatterMatrix(dat[, scales[[currentScale]]])$output$scatterMatrix);
    print(scaleStructureObject[[paste0("Scale Structure for ", currentScale)]]);
  }

```

Reminder: als we straks gemiddelden gaan uitrekenen,
dan moeten we rekening houden met dat er missing values kunnen
en mogen zijn.
  
Reminder: we moeten naar outliers kijken!

## Association matrix of all scales (variables)

```{r }

  ### Als het nog niet goed is, hierboven 'results='asis'' zetten.
  ### results='asis';

  ###verdere outline:
  ###correlation matrix 
  pander(associationMatrix(dat[, names(scales)]));
  ### Temporarily commented out; takes a lot of time.
  #scatterMatrix(dat[, names(scales)])

```

## Correlations between self-identity items

```{r fig.width=8, fig.height=8}
  
  ###filtered: 
  ###nu alleen de benodigde variabelen zonder age etc

  ###factor-analyses (twee variabelen)
  
  ### Inspect correlations between all SI items
  
  selfIdentityItemScatterMatrix <-
    scatterMatrix(dat[, scales$selfIdentity]);
  selfIdentityItemScatterMatrix$output$scatterMatrix$xAxisLabels <-
    names(scales$selfIdentity);
  
  selfIdentityItemAssociationMatrix <-
    associationMatrix(dat[, scales$selfIdentity]);

  print(selfIdentityItemScatterMatrix);
  print(selfIdentityItemAssociationMatrix);
  
  # selfIdentityItemFullFact <-
  #   fullFact(dat[, scales$selfIdentity]);
```

## Factor analyses

```{r}
  

  ### Factor analysis with 1 factor
  fa(dat[, scales$selfIdentity], nfactors=1, fm=faMethod, n.iter=1);
  
  ### Factor analysis with 2 factors
  fa(dat[, scales$selfIdentity], nfactors=2, fm=faMethod, n.iter=1);
  
  ### Parallel analyses
  fa.parallel(dat[, scales$selfIdentity]);
  
  ### Very Simple Structure
  vss(dat[, scales$selfIdentity], rotate='oblimin', fm='minres', n=3);
  
  ### Factor analysis with 3 factor; to verify that it is the third
  ### factor that results in the Heywood case
  fa(dat[, scales$selfIdentity], nfactors=3, fm=faMethod, n.iter=1);
  
  ### So, all evidence points to two factors for this sample.
  ### Now, bootstrap to get factor loadings (and their confidence intervals)
  fa(dat[, scales$selfIdentity], nfactors=2, fm=faMethod, n.iter=n.iter);
  
  ################################################################################
  ### Probably safe to delete
  ################################################################################
  # b <- extractFAloadingsAndCI(a);
  # b <- lapply(b, function(x) { x[, ncol(x) + 1] <- 1:nrow(x); return(x)});
  # 
  # diamondCIplot(b[[1]], yValues=1:nrow(b[[1]]), yLabels=rownames(b[[1]]),
  #               autoSize=NULL, fixedSize=.25);
  # 
  ################################################################################
  ################################################################################
  
  ### For the Self-identity variables in dataframe dat, 
  print(factorLoadingDiamondCIplot(fa(dat[, scales$selfIdentity],
                                      nfactors=2,
                                      fm=faMethod,
                                      n.iter=n.iter),
                                   fixedSize=.15));
  
  ########################################################################
  ### Exploratory factor analyses
  ########################################################################
  
  ### Reasoning conceptual indepence - include in article 
  ### EFAs provide factor loadings. Ideally, these are sufficiently distinct
  ### to show both underlying factors/variables.
  
  ### CFAs provide fit estimates given constraints. If we run a CFA where
  ### we force each item in the corresponding factor (i.e. with a two-factor
  ### structure), we can compare the fit to a one-factor model to determine
  ### conceptual independence.
  
  ### If two concepts (or rather, operationalisations) are independent, then
  ### we would expect the following pattern:
  ###  - items load differentially on the two factors in the EFA (non-overlapping CI's)
  ###  - the two-factor model fits better than the one-factor model


```

## Conceptual independence matrix

```{r message=FALSE, warning=FALSE}

  ### (remove 'message=FALSE, warning=FALSE' above to see warnings, e.g. about Heywood cases)

  headerTable <- makeHeaderTable(c('Factor 1', 'Factor 2'));
  
  ### Reminder: maybe change order of variables
  
  ### Reminder: compare variances of items (homogeneity)
  
  ### Create object for output
  grobsList <- list();
  dfList <- list();
  
  ### Initialize progress bar
  pb <- txtProgressBar(style=3, min = 1, max = length(nonSIvars) ^ 2);
  for (rowVar in names(nonSIvars)) {
    ### Get index of this row
    rowIndex <- which(names(nonSIvars) == rowVar);
    ### Generate object to store the columns of this row in
    grobsList[[rowIndex]] <-list();
    for (colVar in names(nonSIvars)) {
      
      ### Get index of this column
      colIndex <- which(names(nonSIvars) == colVar);
      ### Generate object to store results for this cell in
      grobsList[[rowIndex]][[colIndex]] <-list();
      
      ### Update progress bar
      setTxtProgressBar(pb, (rowIndex - 1 * colIndex) + colIndex);
      
      if (rowVar == colVar) {
        ### On the main diagonal
        grobsList[[rowIndex]][[colIndex]] <-
          textGrob("");
        #        textGrob(paste0("Diagonal of \n", rowVar));
        
        
      } else {
        ### On the upper or lower diagonal
        
        ### Continue with next variable if current two variables
        ### are attitude or importance and attitudeImportance
        if (any(c('attitude', 'importance') %IN% c(colVar, rowVar)) &&
            'attitudeImportance' %IN% c(colVar, rowVar)) {
          
          grobsList[[rowIndex]][[colIndex]] <-
            textGrob(paste0("Skipping this cell!\n(", rowVar,
                            " & ", colVar, ")"));
          
          next;
        }
        
        ### Get a convenient list of variables (items)
        vars <- c(nonSIvars[[rowVar]],
                  nonSIvars[[colVar]]);
        
        ### Get both measurement models
        oneFactor <- paste0(' variable =~ ',
                            paste0(vars, collapse=" + "));
        twoFactor <- paste0(measurementModelSpecs[[rowVar]], "\n",
                            measurementModelSpecs[[colVar]]);
        
        nrOfEFAwarnings <- 0;
        
        ### First do an EFA
#        tryCatch({
          efa <- fa(dat[, vars], nfactors=2, fm=faMethod, n.iter=n.iter);
#      }
                        # warning = function(w) {
                        #   nrOfEFAwarnings <- nrOfEFAwarnings + 1;
                        # },
                        # error = function(e) {
                        #   cat("Fatal error encountered:\n");
                        #   print(e);
                        # });
        
        if (nrOfEFAwarnings) {
          cat0("Encountered ", nrOfEFAwarnings, " warnings.\n");
        }

        nrOfOneFactorCFAwarnings <- 0;

        ### First do an EFA
        #tryCatch({
        oneFactorCFA <- cfa(oneFactor, data=dat);
        #}
        #                 warning = function(w) {
        #                   nrOfOneFactorCFAwarnings <- nrOfOneFactorCFAwarnings + 1;
        #                 },
        #                 error = function(e) {
        #                   cat("Fatal error encountered:\n");
        #                   print(e);
        #                 });
        # 
        # if (nrOfEFAwarnings) {
        #   cat0("Encountered ", nrOfOneFactorCFAwarnings, " warnings.\n");
        # }        

        nrOfTwoFactorCFAwarnings <- 0;

        ### First do an EFA
        #tryCatch({
          twoFactorCFA <- cfa(twoFactor, data=dat);
        #}
        #                 warning = function(w) {
        #                   nrOfTwoFactorCFAwarnings <- nrOfTwoFactorCFAwarnings + 1;
        #                 },
        #                 error = function(e) {
        #                   cat("Fatal error encountered:\n");
        #                   print(e);
        #                 });
        # 
        # if (nrOfEFAwarnings) {
        #   cat0("Encountered ", nrOfTwoFactorCFAwarnings, " warnings.\n");
        # }        

        ### Then run and compare the two CFAs
        cfa <- anova(oneFactorCFA, twoFactorCFA);
        
        ### In cfa$Chisq, the first number is the chi square of the
        ### TWO-factor model, and the second one of the ONE-factor model!
        bestFittingModel <- ifelse(cfa$Chisq[1] < cfa$Chisq[2],
                                   '2-factor', '1-factor');
        
        fitText <- paste0(bestFittingModel, ' fits better; ',
                          'Chisq[',
                          cfa[2, 'Df diff'],
                          ']=', round(cfa[2, 'Chisq diff'], 2),
                          ", ",
                          formatPvalue(cfa[2, 'Pr(>Chisq)']));
        
        ### Make dataframe with factor loading confidence intervals
        faDf <- matrix(unlist(faConfInt(efa)), ncol=6);
        
        ### Set row and column names
        rownames(faDf) <- c(paste0(abbr[rowVar], 1:length(nonSIvars[[rowVar]])),
                            paste0(abbr[colVar], 1:length(nonSIvars[[colVar]])));
        colnames(faDf) <- c(rep(c('lo', 'est', 'hi'), 2));
        
        ### To do: add explained variance per factor
        
        if (rowIndex < colIndex) {
          ### Upper diagonal
          
          grobsList[[rowIndex]][[colIndex]] <-
            faDfDiamondCIplot(faDf, xlab=NULL) +
            ggtitle(paste0(rowVar, ' & ', colVar, "\n",
                           fitText));
          #           textGrob(paste0("Upper diag:\n", rowVar,
          #                           " and ", colVar));
          
        } else {
          ### Lower diagonal
          
          grobsList[[rowIndex]][[colIndex]] <-
            tableGrob(round(faDf, 2));
          
          grobsList[[rowIndex]][[colIndex]] <-
            combine(headerTable,
                    grobsList[[rowIndex]][[colIndex]],
                    along=2);
          
          prevWidths <- grobsList[[rowIndex]][[colIndex]]$widths;
          
          ### Add variable names
          grobsList[[rowIndex]][[colIndex]] <-
            combine(makeHeaderTable(paste0(rowVar, ' & ', colVar), colSpan=6),
                    grobsList[[rowIndex]][[colIndex]],
                    along=2);
          
          ### Set widths (again, based on
          ### https://github.com/baptiste/gridextra/wiki/tableGrob
          grobsList[[rowIndex]][[colIndex]]$widths <-
            unit(rep(.95 * (1/ncol(grobsList[[rowIndex]][[colIndex]])),
                     ncol(grobsList[[rowIndex]][[colIndex]])),
                 "npc");
          
        }
      }
      ### Finally, construct content; for diagonal, omega etc; for
      ### upper diagonal, diamondPlots; for lower diagnoal, numbers
      
    }
  }
  
  ### Close progress indicator;
  close(pb);
  
  CIM <- arrangeGrob(grobs=unlist(grobsList, recursive=FALSE),
                     ncol=length(grobsList));
  
  ### Save conceptual independence matrix
  ggsave(file=file.path(outputPath, paste0('CIM for ',
                                            dataframeName,
                                            '.png')),
         plot=CIM,
         width=100, height=100, units='cm');

```

### Influential cases and regression analyses

```{r}

  
  ################################################################################
  ### Look at influential cases
  ################################################################################
  
  ### regressions
  regr(intention ~ attitude + pbc + perceivedNorms, dat=dat)
  regr(intention ~ attitude + perceivedNorms + pbc + pastBehavior, dat=dat)
  regr(intention ~ attitude + perceivedNorms + pbc + importance + pastBehavior, dat=dat)
  regr(intention ~ attitudeImportance + perceivedNorms + pbc + pastBehavior, dat=dat)
  regr(intention ~ attitude + perceivedNorms + pbc + pastBehavior + currentBehavior, dat=dat)
  regr(intention ~ attitudeImportance + perceivedNorms + pbc + pastBehavior + currentBehavior, dat=dat)
  regr(intention ~ attitude + perceivedNorms + pbc + selfIdentity + pastBehavior, dat=dat)
  regr(intention ~ attitudeImportance + perceivedNorms + pbc + selfIdentity + pastBehavior, dat=dat)
  regr(intention ~ attitudeImportance + perceivedNorms + pbc + selfIdentity + pastBehavior + currentBehavior, dat=dat)
  
  ###studying influencial cases
  
  regrInfluential(intention ~ attitude + pbc + perceivedNorms, data=dat);
  
  regrInfluential(intention ~ attitude + pbc + perceivedNorms + pastBehavior, data=dat);
  
  regrInfluential(intention ~ attitudeImportance + perceivedNorms + pbc + pastBehavior, data=dat);
  
  regrInfluential(intention ~ attitude + perceivedNorms + pbc + pastBehavior + currentBehavior, data=dat);
  
  regrInfluential(intention ~ attitudeImportance + perceivedNorms + pbc + pastBehavior + currentBehavior, data=dat);
  
  regrInfluential(intention ~ attitude + perceivedNorms + pbc + selfIdentity + pastBehavior, data=dat);
  
  regrInfluential(intention ~ attitudeImportance + perceivedNorms + pbc + selfIdentity + pastBehavior, data=dat);
  
  regrInfluential(intention ~ attitudeImportance + perceivedNorms + pbc + selfIdentity + pastBehavior + currentBehavior, data=dat);
  

```

### Structural equation models

```{r fig.width=8, fig.height=8}

  ################################################################################
  ################################################################################
  ### Structural models in SEM
  ################################################################################
  ################################################################################
  
  structuralModels <- list();
  structuralModels$basicRAA <- paste0("### Measurement model \n  ",
                                      measurementModelSpecs$intention, "\n  ",
                                      measurementModelSpecs$attitude, "\n  ",
                                      measurementModelSpecs$perceivedNorms, "\n  ",
                                      measurementModelSpecs$pbc, "\n  ",
                                      measurementModelSpecs$pastBehavior, "\n",
                                      "### Residual correlations \n  ",
                                      "attitude ~~ perceivedNorms", "\n  ",
                                      "attitude ~~ pbc", "\n  ",
                                      "perceivedNorms ~~ pbc", "\n",
                                      "### Structural model \n  ",
                                      "attitude ~ pastBehavior", "\n  ",
                                      "perceivedNorms ~ pastBehavior", "\n  ",
                                      "pbc ~ pastBehavior", "\n  ",
                                      "intention ~ attitude + perceivedNorms + pbc + pastBehavior");

  ### Past (How often) has a negative variance.
  ### We need to understand how this can happen.
  
  ###sem
  ## RAA model without past behavior works, therefore the negative variance should be past behavior

  ################################################################################
 
  structuralModels$basicRAA_nobehav <- paste0("### Measurement model \n  ",
                                      measurementModelSpecs$intention, "\n  ",
                                      measurementModelSpecs$attitude, "\n  ",
                                      measurementModelSpecs$perceivedNorms, "\n  ",
                                      measurementModelSpecs$pbc, "\n  ",
                                      "### Residual correlations \n  ",
                                      "attitude ~~ perceivedNorms", "\n  ",
                                      "attitude ~~ pbc", "\n  ",
                                      "perceivedNorms ~~ pbc", "\n",
                                      "### Structural model \n  ",
                                      "intention ~ attitude + perceivedNorms + pbc");

  ################################################################################

  structuralModels$basicRAA_si <- paste0("### Measurement model \n  ",
                                         measurementModelSpecs$intention, "\n  ",
                                         measurementModelSpecs$attitude, "\n  ",
                                         measurementModelSpecs$perceivedNorms, "\n  ",
                                         measurementModelSpecs$pbc, "\n  ",
                                         measurementModelSpecs$selfIdentitySelected, "\n  ",
                                      "### Residual correlations \n  ",
                                      "attitude ~~ perceivedNorms", "\n  ",
                                      "attitude ~~ pbc", "\n  ",
                                      "attitude ~~ selfIdentitySelected", "\n  ",
                                      "perceivedNorms ~~ pbc", "\n",
                                      "perceivedNorms ~~ selfIdentitySelected", "\n",
                                      "pbc ~~ selfIdentitySelected", "\n",
                                      "### Structural model \n  ",
                                      "intention ~ attitude + ",
                                      "   perceivedNorms + pbc + selfIdentitySelected");

  ################################################################################

  l_ply(names(structuralModels), function(currentModelName) {
    
    currentModel <- structuralModels[[currentModelName]];
    
    cat(currentModel);
    
    lavaanFit <- sem(currentModel,
                     data=dat);

    ### Multigroup SEM
    # lavaanFit <- sem(currentModel,
    #                  data=dat, group='country');
    
    print(summary(lavaanFit));
  
    parameterEstimates(lavaanFit, ci=TRUE, level=.95,
                       boot.ci.type='bca.simple');
    
    ### Plotting only works for one group
    qgraph(semPaths(lavaanFit, "std",
                    edge.label.cex=.8,
                    exoVar = FALSE,
                    curvePivot=TRUE,
                    DoNotPlot=TRUE),
           title = paste0(currentModelName, ", ", dataframeName),
           DoNotPlot=FALSE);
    
  });

  ###Met GJ doen
  ###code controleren die is toegevoegd
  ###correlatiematrix
  ###regressies
  ###toesplitsing op cultuur voor de gehele analyse
  
  ##factor analyses to determine independency of the determinants
  

```
